\section{Fluctuations}
% BURDE VÆRE SUBSECTION
Later we will come back to how we correct the mean field approximations to \(\Sa_{\text{eff}}[a^\dagger, a]\). We can do this by developing to Gaussian order  (2.order) in the fluctuations in the boson fields \(a^\dagger, a\), near the saddle point. A coarse structure of this will be the following. Define 

\begin{equation}
A = 
\begin{pmatrix}
\delta a^\dagger \\
\delta a
\end{pmatrix}, 
A^\dagger =
\begin{pmatrix}
\delta a & \delta a^\dagger
\end{pmatrix}
\end{equation}

\begin{align}
\Sa_{\text{eff}} &\simeq \Sa_{\text{MF}} - \sum_q A^\dagger D^{-1}(q)A \nonumber\\
\Z &\simeq \e^{\Sa_{\text{MF}}}\int\D A^\dagger\D A\e^{- \sum_q A^\dagger D^{-1}A}\nonumber  \\
\Z &= \e^{\Sa_{\text{MF}}}\e^{-\Tr\ln D^{-1}} \label{eq:partition_fluctuations}
\end{align} where $D^{-1}$ is a \(2\times 2\) matrix. A constraint (claim) to stability of the saddle point is that $D^{-1}$ have to be positive definite, i.e. it must have only positive eigenvalues. 
With $\Z = \e^{-\beta F}$  we have 

\begin{equation}
\label{eq:free_energy_fluctuations}
F = F_{\text{MF}} + \frac{1}{\beta}\Tr\ln D^{-1}.
\end{equation}
We can now correct  the mean field values for $a, a^\dagger$ by minimizing \eqref{eq:free_energy_fluctuations} with respect to $a, a^\dagger$.

\begin{equation}
\pdv{F}{a} =0 = \pdv{F_{\text{MF}}}{a} + \underbrace{\pdv{a}\left(\frac{1}{\beta}\Tr\ln D^{-1}\right)}_{\text{Correction term}}.
\end{equation}

This means that we can find the fluctuation corrections to $T_c$ etc. We expect these corrections to be significant when $T_c$ becomes large. As of October 1996', no such calculations on the fluctuations has been made.\footnote{As of 2019, it has probably been done thoroughly.}